\documentclass{article}
\usepackage[a4paper, total={6in,9in}]{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\begin{document}
\pagestyle{fancy}
\fancyhead[L]{CS1010 -- Intro to Information Technology}
\fancyhead[R]{HW 4}

\section*{Description}
On collab, there are two files for HW4: this file HW4.pdf and HW4.py. To receive full credit,
complete all three challenges listed in HW4.py and answer each accompanying question on HW4.pdf.
Complete your challenges in the HW4.py file and submit this along with your answer to the questions.
Failing to submit your code this way will result in a deduction of 1 point. You are allowed to discuss
the programming challenges with your classmates and use resources, like the internet, for help, but
you must write your own code. If you discuss problems with a classmate, please list their name
on the Collaborator's line on HW4.py (line 4). If you use any resources, please list them on the
resources line. If it's a website, provide the link.

\bigskip

\begin{center}
Once again, \textbf{you must write your own code.}    
\end{center}

\section*{Challenge 1 (1 Pt)}
When you printed out the set, why did it have fewer items in it than the list it came from?
\vspace*{2.5in}

\section*{Challenge 2 (1 Pt)}
How did you keep track of which input was the longest?
\vspace*{2.5in}

\section*{Challenge 3 (2 Pt)}

\begin{enumerate}
    \item Run the code for this challenge and report the input and output. Prove it is not working as intended (What would you expect given the inputs?): \vspace*{2in}
    \item \begin{enumerate}
        \item Was the issue with adding numbers to the list? If so, what was the issue? How did you check? \vspace*{1.75in}
        \item Was the issue with computing the sum? If so, what was the issue? How did you check? \vspace*{1.75in}
        \item Was the issue with computing the average from the sum? If so, what was the issue? How did you check?
    \end{enumerate}
\end{enumerate}

\end{document}